Activities

### 2025-09-19 activities.qmd
after Roes, typo corrected (GH 250918)
add Roes slides Theresa (GH 250919)

* Invited session at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Contrasting Bayesian and frequentist model building for descriptive research questions - a paired-design experiment of STRATOS-TG2. Invited speaker: [Mariana Nold](/assets/Mariana_slides_Roes_2025.pdf). Further speakers for TG2: [Michael Kammer](/assets/20250902_Kammer.pdf), [Aliaksandr Hubin](/assets/Aliaksandr_slides_Roes_2025.pdf), [Georg Heinze](/assets/2025-09 Roes Heinze.pdf).

<details>
  <summary>Session abstract and slides</summary>

@@

* Invited talk at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Towards best practices in medical statistics: The need to implement innovative scientific solutions. Speaker: Theresa Ullmann. Topic of the talk: Neutral Comparisons Of Statistical Methods: Opportunities, Challenges, And Common Issues (Includes as an example TG2-P11, Simulation study on variable selection)

>>>>

* Invited session at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Contrasting Bayesian and frequentist model building for descriptive research questions - a paired-design experiment of STRATOS-TG2. 
Invited speaker: <a href="/assets/Mariana_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Mariana Nold</a>. 
Further speakers for TG2: <a href="/assets/20250902_Kammer.pdf" target="_blank" rel="noopener noreferrer">Michael Kammer</a>, 
<a href="/assets/Aliaksandr_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Aliaksandr Hubin</a>, 
<a href="/assets/2025-09 Roes Heinze.pdf" target="_blank" rel="noopener noreferrer">Georg Heinze</a>.

<details>
  <summary>Session abstract and pictures</summary>

@@

* Invited talk at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Towards best practices in medical statistics: The need to implement innovative scientific solutions. Speaker: Theresa Ullmann. Topic of the talk: [Neutral Comparisons Of Statistical Methods: Opportunities, Challenges, And Common Issues](assets/Slides ROeS Ullmann.pdf) (Includes as an example TG2-P11, Simulation study on variable selection)
